Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory:  the case of distributed recycling at Nancy, France

### 2021-11-29 00-ES/PubliER/PubliER.Rmd
avancando hoy

---
title: "Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory:  the case of distributed recycling at Nancy, France"
#documentclass: extarticle
#fontsize: 14pt
geometry: "left=3cm, right=3cm,top=3cm,bottom=2cm"
author:
  - name: Fabio A. Cruz
    email: cruzsanc1@univ-lorraine.fr
    affiliation: UTT
    footnote: 1
  - name: Nadège Troussier
    #email: bob@example.com
    affiliation: UTT
  - name: Hakim Boudaoud
    #email: cat@example.com
    affiliation: UL
    #footnote: 2
  - name: Mauricio Camargo
    #email: derek@example.com
    affiliation: UL
    #footnote: 2
address:
  - code: UTT
    address: "Universite de Technologie de Troyes, Troyes, France"
  - code: UL
    address: "ERPI, Université de Lorraine, F-54000 Nancy, France."
footnote:
  - code: 1
    text: "Corresponding Author"
journal: "PubliER2022 - The industry of the future : beyond the Anthropocene. 2-4 Feb 2022 Troyes (France)"
date: "`r Sys.Date()`" 
csl: journal-of-cleaner-production.csl
output: rticles::elsevier_article
# author:
# - Fabio A. Cruz Sanchez^[Université de Lorraine]
# - Nadège Troussier^[Université Technologique de Troyes]
# - Hakim Boudaoud^[Université Technologique de Troyes]
# - Mauricio Camargo^[Université Technologique de Troyes]
# date: "`r format(Sys.time(), '%d %B %Y')`"

# output:
#   bookdown::pdf_document2:
#     toc: true
#     keep_tex: TRUE
    #pandoc_args: "--latex-engine-opt=--shell-escape"
  # bookdown::html_document2: default
  # bookdown::word_document2: default
#output: rticles::tf_article
abstract: |
    <!-- Intro -->
    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
    <!-- Problem -->
    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
    From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
    <!-- Conceptual Framework (broad theoretical) -->
       <!-- ES valuation and Urban  ES-->
    On the ecological side, there have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES).
       <!-- LCA -->
    While on the industrial side, life cycle assessment (LCA) tool is focused on the quantification of the environmental impact of industrial interventions. Despite its ability to cover mutually exclusive and exhaustive impact categories, the LCA approach still has deficiencies: 1) it focuses on quantifying and reducing the net environmental impacts, but not on reducing ecological overshoot and establishing synergies with nature; 2) it considers the interactions between technological processes, but not the interactions between relevant ecosystems.
    <!-- Knowledge Gap -->
    Few researches have addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
    There is a need to include the ES in the desicion making process to establish the capacity of the territory in order to evaluate an absolute environmental sustainability of industrial systems. 
    <!-- Logic & Evidence for Problem, KG and Context -->
          <!-- LCA AND ES -->
    <!-- Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales.
    This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature. -->
    <!-- Purpose Statement -->
    The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
       <!-- Expand a methodology -->
    A prioritization is made based on the connection of urban ES services and the techno-ecological synergy.
    The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
    <!-- Context -->
    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework for the territory of Nancy, France. 
    The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
always_allow_html: true
# editor_options: 
#   markdown: 
#     wrap: 100
bibliography: library.bib
#bibliography: References.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
  \usepackage{tabu}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%')
options(knitr.kable.NA = '')
#options(tinytex.engine_args = '--shell-escape')

library(readxl)
library(here)
library(tidyverse)
library(flextable)
library(rsvg)
set_flextable_defaults(fonts_ignore=TRUE)

@@

```{r, include=FALSE}
knitr::knit_exit()
```

@@

<!-- ## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity. -->
<!-- Intro -->
The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
<!-- Technological development claiming sustainabiilty -->
Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs [@ref].
For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
This meta-principle is a imperative but not sufficient condition for sustainability.
Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@ref].
We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
<!-- Gap in the literature -->
However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.

<!-- Sustainability frameworks -->
@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level. 
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
<!-- They hightligthed that differens Systemic design approaches are   -->

<!-- Importance of ES in the Engineering -->
The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare. 
However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
  <!-- Engineering blindness -->
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal. This scenario is not true today.
  <!-- Engineering withing ecological constraints -->
The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
 <!-- Importance of ES in the decision making process -->
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
It is difficult to provide information about pressure from industrial systems in corporate information systems. 
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].

@@

<!-- The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017]. -->
<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.  -->

The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems. 
This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements. 
  <!-- Case study -->
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
Therefore, new approaches need to be explored in order to reduce ar at least recycling this material. 
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

The expected results seek to address the following questions:

- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? 
- How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory? 
From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators   for deployments distributed recycling approach,

In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.

\textcolor{red}{The article is structure as follows.... ( to complete) } section \@ref(background) ...

<!-- The Green Fablab at LF2L is considered as case study to put in practice the development of a methodological framework considering sustainability dimensions, derived from the implementation of a distributed plastic recycling chain.  -->

# Background
\label{background}

## Ecosystem services

<!--# Intro -->
Foundational ideas on ecosystem services seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002]. 
Today, ecosystems services field are being included in the decision-making through promotion of market Based Instruments for Payment for Ecosystems services schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
Nevertheless, commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs.
Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].

<!--# Definition of Ecosystem Services -->
Ecosystem services (ES) are the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017]. Ecosystem goods (e.g; Food) and services (e.g. waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997]. 
  <!--# Functions vs Services -->
It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself. The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits. 
By contrast, the latter are those processes and functions where people can (or could have the potential [@ref]) obtain benefits. The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach. Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@ref]. 
One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003]. This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders [@Honeck2021].

<!--  Research themes in ES -->
Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field. 
Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.

Efforts have been made in the literature to classify the methods used to assess ecosystem services based on 27 case studies. Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative.

<!--# Classification of ES -->
Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
In the heart of the four main, they share four main categories of ES:
**Provisioning** (e.g. food and medicines); 
**Regulating** (e.g. pollination and climate regulation), 
**Supporting** (e.g soil formation and fixation of solar energy) and 
**Cultural / Information** services (e.g. artistic inspiration and recreation) services are four broad catagories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].

@@

The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings [70]. 
With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings. 
The product-based CICES framework can enable clearer mapping between ecological and economic products. 
The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level. 
The following levels organize ES according to their divisions, groups and classes. 
At lower levels, more specific services can be defined and characterized. 
For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed. 
Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.

Figure 2.2 demonstrates the hierarchical structure of CICES scheme.

# Methodology

The purpose of this article is to evaluate the supply and demand of eecosystem services for a prospective distributed recycling chain for additive manufacturing.
A conceptual framework to evaluate the synergy of prospective industrial filières considering the technological and ecological spheres.

@@

  <!-- Step 1 Assessments-->
The goal of *Planning* step is to identify the boundaries for the technological and ecological systems to be evaluated.
  <!-- Step 2 Plannig-->
In the *Assessment* step, the main aim is to jeopardize the key ecosystems services and the respective scales that are going to be included in the analysis. 
These elements will be a intersection of the technological and geographical issues based on a analysis of each systems.
  <!-- Step 3 Evaluate-->
In the *Evaluation* stage, the main purpose is to establish the demand and supply of ES based on respective inventory and models. This include the specific allocation
  <!-- Step 3 Management-->
Finally, in the last step *Management*, the main goal is to establish scenarios of evaluation based on the 'Bussiness-as-usual' and Synergy frameworks.
This will enable to take a more informed decision to stakeholder at the evaluation of prospopective projects.

An application of the framework will be presented in Section XX using as case study of the distributed recycling chain via additive manufacturing..
In the following sub-sections, each stage of the methodology is explained.

# Results

@@

The goal of this first step is to highlight the main interactions (positive and negative) that the

@@

>>>>

---
title: "Integrating and prioritizing ecosystems services at early development stages of industrial systems in a territory:  the case of distributed recycling at Nancy, France"
#documentclass: extarticle
#fontsize: 14pt
geometry: "left=3cm, right=3cm,top=3cm,bottom=2cm"
author:
  - name: Fabio A. Cruz
    email: cruzsanc1@univ-lorraine.fr
    affiliation: UTT
    footnote: 1
  - name: Nadège Troussier
    #email: bob@example.com
    affiliation: UTT
  - name: Hakim Boudaoud
    #email: cat@example.com
    affiliation: UL
    #footnote: 2
  - name: Mauricio Camargo
    #email: derek@example.com
    affiliation: UL
    #footnote: 2
address:
  - code: UTT
    address: "Universite de Technologie de Troyes, Troyes, France"
  - code: UL
    address: "ERPI, Université de Lorraine, F-54000 Nancy, France."
footnote:
  - code: 1
    text: "Corresponding Author"
journal: "PubliER2022 - The industry of the future : beyond the Anthropocene. 2-4 Feb 2022 Troyes (France)"
date: "`r Sys.Date()`" 
csl: journal-of-cleaner-production.csl
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
  #pandoc_args: "--latex-engine-opt=--shell-escape"  
  # bookdown::html_document2: default
  # bookdown::word_document2: default

abstract: |
    <!-- Intro -->
    Ecosystem services (ES) is a powerful conceptual framework to put in evidence the benefits that humans receive from nature, most of time for free.
    <!-- Problem -->
    The problem is that it is complex to link between the local ecosystem services of an urban territory and the industrial systems placed within it, identifying the priority interactions (as synergy and impacts).
    From a decision-maker perspective, there is no a aid decision tool to guide a multicriteria evaluation at early development stages of industrial systems.
    <!-- Conceptual Framework (broad theoretical) -->
       <!-- ES valuation and Urban  ES-->
    On the ecological side, there have been major efforts in the valuation of ES given by ecosystems (terrestrial, aquatic, atmospheric) to the human well-being and great advances in the developing of a standard ES baselines such as Common International Classification of Ecosystem Services (CICES).
       <!-- LCA -->
    While on the industrial side, life cycle assessment (LCA) tool is focused on the quantification of the environmental impact of industrial interventions. Despite its ability to cover mutually exclusive and exhaustive impact categories, the LCA approach still has deficiencies: 1) it focuses on quantifying and reducing the net environmental impacts, but not on reducing ecological overshoot and establishing synergies with nature; 2) it considers the interactions between technological processes, but not the interactions between relevant ecosystems.
    <!-- Knowledge Gap -->
    Few researches have addressed the alignment the territorial priorities in terms of ES for planning and urban development with the supply/demand of ES by industrial systems.
    There is a need to include the ES in the desicion making process to establish the capacity of the territory in order to evaluate an absolute environmental sustainability of industrial systems. 
    <!-- Logic & Evidence for Problem, KG and Context -->
          <!-- LCA AND ES -->
    <!-- Recently, several research efforts reported  accounts for the dependence systems by explicitly accounting for the demand that technological systems place on ecosystems and the supply of ecosystem services that nature can provide to a process or product at multiple spatial scales.
    This techno-ecological synergy (TES) [@Liu2019g; @Bakshi2015] to reflect its emphasis on establishing mutually beneficial or synergistic relationships between technological and ecological systems, with the ultimate goal of achieving harmony between human activities and nature. -->
    <!-- Purpose Statement -->
    The purpose of this article is to propose a methodological approach in order to include ecosystem services in regarding the territorial and industrial endeavors.
       <!-- Expand a methodology -->
    A prioritization is made based on the connection of urban ES services and the techno-ecological synergy.
    The results of are step forwards to create techno-ecological synergies between ecological and industrial systems.
    <!-- Context -->
    This methodological steps will applied to the case of distributed recycling via additive manufacturing (DRAM) to highlight the relevant ES from the CICES framework for the territory of Nancy, France. 
    The technical advancements of recycling approaches using additive manufacturing are promising technical interventions to foster plastic recycling at a local level.
always_allow_html: true
bibliography: library.bib
link-citations: yes
linkcolor: blue
header-includes: |
  \usepackage{float}
  \usepackage{subfig}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
  \usepackage[bitstream-charter]{mathdesign}
  \usepackage{pdflscape}
  \usepackage{svg}
  \usepackage{lineno}
  \usepackage{setspace}
  \newcommand*{\doverline}[1]{\overline{\overline{#1}}}
  \usepackage{tabu}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.retina = 3, message = FALSE, warning = FALSE, out.width='100%', cache = FALSE)
options(knitr.kable.NA = '')
#options(tinytex.engine_args = '--shell-escape')

library(readxl)
library(here)
library(tidyverse)
library(flextable)
library(rsvg)
library(kableExtra)
set_flextable_defaults(fonts_ignore=TRUE)

@@

```{r, include=FALSE}

@@

<!-- ## Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity. -->
<!-- Intro -->
The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the $21^{st}$ century [@Lomborg2020].
<!-- Technological development claiming sustainabiilty -->
Even though engineering products and processes might meet the needs of the present society, many of the technological developments are compromising the ability of future generations to meet their own needs [@Bakshi2019a].
For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity  [@Bakshi2018]. 
This meta-principle is a imperative but not sufficient condition for sustainability.
Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries [@ONeill2018].
Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution [@Diwekar2021].
We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems. 
<!-- Gap in the literature -->
However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.

<!-- Sustainability frameworks -->
@Ceschin2016 putted forward the evolution of *Design for Sustainability (DfS)* framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level. 
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
<!-- They hightligthed that differens Systemic design approaches are   -->
@SousaRocha2019 revealed ten different models at operational, tactical, and strategical levels
<!-- Importance of ES in the Engineering -->
One strategical point in sustainability relies on the economic valuation of ecosystem goods and services framework. This approach gives an elegant framework highlighting their importance for society and human welfare. 
However, there is a need to explicitly account for their contribution when designing and developing products and services [@Diwekar2021].
  <!-- Engineering blindness -->
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity  to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the  human activites' impacts on the earth remained marginal. This scenario is not true today.
  <!-- Engineering withing ecological constraints -->
The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital [@Torres2021].
 <!-- Importance of ES in the decision making process -->
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers [@Bruel2018]. 
It is difficult to provide information about pressure from industrial systems in corporate information systems. 
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on [@Bakshi2018].

@@

The main purpose of this article is to propose a methodology in order to  prioritize the ecosystem services at early development stages of industrial systems in a territory.
This methodology is based in the use of the ecosystem services as boundary object [@Abson2014] with the purpose to identify ES according to the perspective of global value chain, industrial chain and territorial perspective. 
  <!-- Case study -->
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms [@Kumar2021].
Therefore, new approaches need to be explored in order to reduce or at least recycling this material. 
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory. 
<!-- Expected results -->
The expected results seek to address the following questions:

- What are the appropriate ecosystem service indicators for assessing an prospective filière as distributed plastic recycling? - How does the implementation of a distributed plastic recycling chain impact on ecosystem services? 
- What are the barriers and drivers for the development of a distributed plastic recycling chain in a territory?

From a perspective of strong sustainability, we look to identify a set of principles, criteria and indicators for deployments distributed recycling approach.
In a methodological level, the expected in goals concern to the creation of decision-tools to informed decisions about real impact of industrial systems in a territory.
This start by raising awareness of the dependence of natural capital in the technology system towards quantification and valuation of technological impacts on ecosystems.

The article is structure as follows. 
Section \@ref(background) presents a background on theoretical element of ecosystem service in link with life cycle assessment and the territorial planning.
Section \@ref(methodology) presents the methodology proposed to identify and prioritize the ecosystems services. 
In Section \label{results}, the results of the methodology are presented for the industrial system of distributed recycling for additive manufacturing at Nancy, France. 
This industrial case enable to highlight the pertinence and limits of the methodology.

# Literature Review
\label{background}

## Ecosystem services and the global value chain

<!--# Intro -->
Foundational ideas on ecosystem services (ES) seek for conceptual and methodological tools with the major goal to increase public interest in biodiversity conservation through the recognition, accounting and valuation of the societal dependence on the ecological life support systems for the human well-being [@Gomez-Baggethun2010; @DeGroot2002]. 
<!--# Definition of Ecosystem Services -->
ES describes the ecological characteristics, function or processes that contribute (actively or passively) to the human well-being [@Costanza1997; @Costanza2017]. 
Ecosystem goods (e.g; Food) and services (e.g. waste assimilation) illustrate the benefits that human derive from the ecosystem functions [@Costanza1997]. 
<!--# Functions vs Services -->
It is needed to distinguish between the ecosystem's functions and processes from the ecosystem services concept itself. 
The former describes biophysical relationships that are carried out by nature regardless of whether or not human benefits. 
By contrast, the latter are those processes and functions where people can (or could have the potential) obtain benefits. 
The ecosystem services do not flow to human well-being without crucial interactions with the different forms of capital (Natural, Social, Human, Built), which entails the need of understanding, modelling, measuring, and managing ES in a trans-disciplinary approach. 
Likewise, the concept of ecosystem dis-service denotes the processes and functions that affect humans in 'negative' way, making damage and costs [@TEEB2010]. 
One major point that ES make clear is to raise awareness on the recognition of humanity's primary dependencies on the 'functions of' natural capital which reflects the fact that, however they may perceive themselves, humans are part of, and not apart from, nature [@Ekins2003]. 
This entails the necessity to create knowledge for trans-disciplinary approaches using ES as boundary object for sustainability for diverse stakeholders [@Honeck2021].

<!--  Research themes in ES -->
Using a systematic literature review approach, @Torres2021 distinguished and categorized 8 major key themes and 22 approaches in the ES field. Key themes represent underlying meanings or ideas that are widely used, trending or rising in the ecosystem services research field. 
Key approaches include methods [@Harrison2018], tools, frameworks, perspectives and management strategies to analyze, assess, and quantify ecosystem services.
It was reported that, computational modelling and non-monetary valuation are emergent topics that appear to be trending upwards in terms of interest.
   <!-- Conclusion of ES research -->
Today, ecosystems services field are being included in the decision-making through promotion of market-based instruments for payment for ES schemes with the purpose of create and environmental governance according to the reality of impact on the natural capital [@Laurans2013].
Nevertheless, the commodification of nature's services by reductionist thinking about  individual services runs the risk of unintended harm and unbalanced outputs [@Gomez-Baggethun2010].
Systems thinking is essential for avoiding such harm [@Gopalakrishnan2016].

## Common standard of ecosystem services

<!-- Efforts have been made in the literature to classify the methods used to assess ecosystem services. Ecosystem service assessment methods were classified into four broad categories: biophysical, socio-cultural, monetary, and integrative. -->

<!--# Classification of ES -->
Different initiatives have been reported to classify the ES, including the Millennium Ecosystem Assessment [@MEA2005], 
The Economics of Ecosystems and Biodiversity TEEB [@TEEB2010],
The Intergovernmetal Plastform of Biodiversity and Ecosystem Services (IPBES) [@ref] and the Common International Classification of Ecosystem Services (CICES). 
In the heart of the four main, they share four main categories of ES:
**Provisioning** (e.g. food and medicines); 
**Regulating** (e.g. pollination and climate regulation), 
**Supporting** (e.g soil formation and fixation of solar energy) and 
**Cultural / Information** services (e.g. artistic inspiration and recreation) services are four broad categories types of ES constitutes the core of most recent classifications and that are shared by the most frameworks [@PedersenZari2019].

@@

The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings [70]. 
With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings. 
The product-based CICES framework can enable clearer mapping between ecological and economic products. 
The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.

The following levels organize ES according to their divisions, groups and classes. 
At lower levels, more specific services can be defined and characterized.

For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.

Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.

## Ecosystems services and industrial systems: Towards a synergy between

One major point A holistic evaluation of the externalities that industrial system 
Ecosystems services and industrial systems need to be confronten to holistic evaluation
The key point for bussiness and government sectors in terms realize an integrated valuation and comprehensive account of both the negative impacts on ES from business activites and the positive contributions of ES to business and households [@Costanza2017].

<!-- More general, the critical issues relies on the importance of ES to challenge the conventional approaches to growth and development, towards a perspective more focalized on the prosperity and wellbeing.  -->

## Ecosystems services at the urban territorial planification

<!-- Urban Ecosystem Services -->
More than two thirds of the world's population are expected to live in cities by 2050 [@ref]. 
Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities [@Gomez-Baggethun2013].
  <!-- Importance of Urban ES -->
Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
cooling, and runoff mitigation [@Bolund1999]. 
  <!-- Classification of Urban ES -->
@Gomez-Baggethun2013 draws on the developments of the ecosystem services for urban planning. 
They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.

# Methodology
\label{methodology}

The purpose of this article is to identify main relevant ES services from a industrial and territorial perspective at the early design of industrial systems. 
This identification is a first step with the purpose to evaluate the supply and demand of ecosystem services for these industrial systems.

@@

- **I) Global value Planning**: the main goal is to identify the the links between the global value chain to be evaluated and the capital nature through the literature on ecological systems.
The main purpose in this step is to map the the interactions positive and negative.

- **II) Industrial system**: the main aim is to define the technosphere and identify the key ecosystems services that are impacted. 
The identification is made using the lens of connection between the LCA and ES elements.

- **II) Industrial system**: in this step, the main purpose is the identification of the key urban priorities in the territorial context from a perspective of ecosystem services.
To establish these priorities, the territorial planification perspective is analysed given the fact that a particular city varies greatly in function of the environmental and socio-economic characteristics of the territory.

- Finally, in **IV) Synthesis**, the main goal is to converge on main ES that are identified for the three last perspectives,

In the following sub-sections, each stage of the methodology is explained.
An application of the framework will be presented in Section \label{results} using as case study of the distributed recycling chain via additive manufacturing.

# Results
\label{results}

 Context of the industrial system

 A prospective distributed recycling chain for additive manufacturing .

@@

The goal of this first step is to highlight the main interactions that the value chain have with the natural ecosystems.
This enables us to have a holistic picture of the impacts of plastic pollution in the natural ecosystems taking into account the highlighting the uncertainties and knowledge gaps that could exist in the field.

```{r fig-Kumar2021, fig.cap= 'Illustration of MPs and NPs affecting various ecosystem services and climate change on terrestrial, aquatic, and atmospheric ecosystems. Source. Kumar2021.jpg' }

#download.file(paste0(URL,'Plastics/ES/Kumar2021.jpg'), "Figures/Kumar2021.jpg")

knitr::include_graphics('Figures/Kumar2021.jpg')

@Kumar2021 reported a complete description of the major impacts on the plastic pollution an the ecosystems services,identifying in what extend there are present the interlinkages between plastic pollution, waste management, and Sustainable Development Goals (SDG).
  <!-- Presenting the Figure -->
Figure \@ref(fig:fig-Kumar2021) presents an overview of the major interactions that plastic impact the ecosystem services in the terrestrial and aquatic ecosystems, representing a major societal issue.
Macrosplastics -MP- (particules $\geq 5mm$ ), mesoplastics -MsP- ($1-5 mm$) and microplastics ($<1~mm$) are the major problems in the ecosystems.

For aquatic ecosystems, main risks are linked to standing water that acts as a breeding niche (to mosquitoes, pests, vector-borne diseases transmission), becomes a vector for toxic chemicals and, ultimately, disturbs the natural cycles (biogeochemical cycle in terrestrial ecosystems). Additionally, the transfer of  plastic into the food chain is a clear danger to animal and, certainly, to humans as well. Thus, reducing the consumption of plastics is of great importance in the long term.

The plastic value chain is one of the mo

- Plastic materials have impats on the terrestrial, qauqtic, and atmospheric ecosystems.

-

Concerning the terrestrial impacts, the plastic degradation make and important impact on the pollitation of the

@@

\renewcommand{\arraystretch}{1.5}
```{r Value-chain-ES, include=TRUE}

Value_chain <- 
  tribble(
  ~Description, ~ES, ~Ref,

# Provisioning (Biotic)
  'Soil productivity is impacted due to the nutrient imbalance followed by oxidative stress and leading to the poor growth of food crops',
  '1.1.1.1 ; 1.2.1.1', 
   '[@Kumar2021]',

'MPs and their suspended solids hasten eutrophication. Eutrophication worsens as a result of both resuspension and algae growth, adding more contaminants to the food chain supply and primarily creating organic contamination.', 
  '1.1.5.1 ; 1.1.6.1 ', 
    '[136]',

# Regulation & Maintenance (Biotic)

  'MPs and NPs in the atmosphere also lead to the obstruction and lowering of pollination.',
  '2.2.2.1',
    '[@Kumar2021]',

"MPs and NPs are established to act as a vector and breach through any system (organisms) and even via trophic transfer (one trophic level to another via food chain), therefore, it can be hypothesized that MPs in the future can play a pivotal role in the spill over of infectious diseases, leading to an epidemic or pandemic of unknown scale",
  '2.2.3.1; 2.2.3.1',
  'Ref',

  'MP and NP in terrestrial ecosystems reduce tha ability to sequester carbon.',
    '2.1.1.2 ; 2.2.4.1', 
      '[@Kumar2021]',

  'Elements as nitrogen and phosphorous, are also vividly influenced due to MPs and NPs in the soil ecosystem',
    '2.2.4.1 ; 2.2.4.2',
      '[@Kumar2021]',

    "MPs accumulation can promote mineralization, nitrification, and denitrification in aquatic ecosystems, therefore releasing CO2, CH4, and N2O.",
    '2.2.6.1',
      '[@Kumar2021]',

  'marine carbon sinks are critical in analyzing the global climate change and are potentially affected by MPs and NPs pollution on phytoplankton-sequestered CO2 and their transmission to the deep ocean via zooplankton [77].',
    '2.2.5.2 ',
    '[@Kumar2021]',

  'Plastics-induced variations in solar radiation in the water column can alter physical processes at the ocean’s surface and near-surface layers as well as trigger climate feedback mechanisms',
    '2.2.6.1',
    '[@Kumar2021]',

  'MPs and NPs are known to cause a dynamic shift in the soil temperature as is commonly practiced in agriculture sectors with extreme climatic conditions.', 
    '2.2.4.1',
    '',
